---
title: "practicum2"
author: "Anna Calle"
date: "5/2/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r load, echo=FALSE}
# Load the required packages
library(DeclareDesign)
library(knitr)
library(ggplot2)
library(grid)
library(gridExtra)
library(dplyr)
library(kableExtra)
```

## Measurement Goal & Measure

**Goal**: Assess the level of satisfaction of donors with the program.

"How satisfied are you with the restoration work done by The Freshwater Trust?"

a. Very Satisfied
b. Somewhat Satisfied
c. Somewhat Unsatisfied
d. Very Unsatisfied
e. Don't Know


## Source & Rationale & Unit

*Source*:

*Rationale*: 

*Unit*: individual survey respondent


## Responsibility & Frequency

*Responsibility*: 

*Frequency*: 


## Declaring the population



## Target Population & Challenges

*Target Population*: individuals who have made donations

*Challenge of drawing a representative sample*: donors satisfied with the program are more likely to respond than unsatisfied donors, creating a response bias

*Sampling procedure*: Stratified samplying of on-time donors and recurring donors

## Conceptual practice: stratification



## DeclareDesign()

```{r declare-pop}
set.seed(8) 
population <- declare_population(
  donors = add_level(N=500, 
     recurring=draw_binary(N=N, prob = 0.5),
     satisfied=correlate(given = recurring, rho = 0.5,
                         draw_binary, prob = 0.5)
))

my_estimand <- declare_estimands(mean(satisfied),
                                 label = "Ybar")
```

## DeclareDesign()

```{r declare-report}
reporting <- declare_assignment(blocks=recurring,
                  assignment_variable = "R",
                  block_prob=c(0.2,0.5))

sampling <- declare_sampling(strata=recurring,
                             strata_n=c(175,75))

```

## DeclareDesign()

```{r declare-estimator}

strata_weighted_mean <- function(data){
  data.frame(  
  estimator_label = "strata_w_mean",
  estimand_label = "Ybar",
  n = nrow(data),
  stringsAsFactors = FALSE,
  
  estimate = data %>% filter(R==1) %>%
    group_by(recurring) %>% 
    summarise(mean=mean(satisfied)) %>%
    mutate(prop=c(0.5,0.5)) %>%
    mutate(sub.mean=mean*prop) %>% pull(sub.mean) %>% 
    sum())
} #just use this function, custom

```

## DeclareDesign()

```{r diagnosis, cache=TRUE}

answer <- declare_estimator(
  handler = tidy_estimator(strata_weighted_mean),
  estimand = my_estimand)

design <- population + my_estimand + reporting +
          sampling + answer
diagnosis <- diagnose_design(design, sims = 1000)

diagnosis$diagnosands_df[,c(4,5,12,14)] %>%
  kable()

```




